Insight Into Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-08-18 draft.tex
Summary and Future Work

\section{\uppercase{Conclusion}}
\label{sec:Conclusion}
The presented results indicate that the parameters torsion, curvature and curvature angle are not enough to characterize pathological changes in the lumbar spine.
%%
They are well suited to characterize subject gender due to their height difference using mean curvature and mean curvature angle.
%%
The reason for this lies in the higher curvature of smaller subjects and the significant difference of average body size between males and females.
%%
Gender was characterized well in the analysis of all subjects as well as subjects divided by age.

@@

Another observation during the analysis are very large decision trees achieving low error scores.
%%
Their complexity impose overfitting to the data and they are not suitable for extracting universal rules.
%%
\subsection{Proposed Features}
\begin{figure}[!h]
  %\vspace{-0.2cm}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/placeholder}
  \caption{Proposed features. (a) dented vertebraes are a sign of heavy stress and bone absorption. (b) Spine canal thickness is associated with herniated disks. (c) the spine canal shape can be used to characterize scoliosis and lordosis as well as the \emph{Cobb-Angles} \cite{Cobb}. }
  \label{fig:proposedFeatures}
\end{figure}
%%
\noindent Pathological deformation of the lumbar spine is usually the last stage and is associated with very strong lower back pain \com{Zitat Frau Hegenscheid fragen}.
%%
We have to capture earlier signs of pathological change in order to derive better predictive models.
%%

@@

>>>>

\section{\uppercase{Conclusion}}
\label{sec:Conclusion}
\noindent The presented results indicate that the parameters torsion, curvature and curvature angle are not enough to characterize pathological changes in the lumbar spine.
%%
They are well suited to characterize subject gender due to their height difference using mean curvature and mean curvature angle.
%%
The reason for this lies in the higher curvature of smaller subjects and the significant difference of average body size between males and females.
%%
Gender was characterized well in the analysis of all subjects as well as subjects divided by age.

@@

Another observation during the analysis are very large decision trees achieving low error scores.
%%
Their complexity impose overfitting to the data and they are not suitable for extracting universal rules.
%%
\subsection{Proposed Features}
\label{sec:ProposedFeatures}
\begin{figure}[!h]
  %\vspace{-0.2cm}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/placeholder}
  \caption{Proposed features. (a) dented vertebraes are a sign of heavy stress and bone absorption. (b) Spine canal thickness is associated with herniated disks. (c) the spine canal shape can be used to characterize scoliosis and lordosis as well as the \emph{Cobb-Angles} \cite{Cobb}. }
  \label{fig:proposedFeatures}
\end{figure}
%%
\noindent Pathological deformation of the lumbar spine is usually the last stage and is associated with very strong lower back pain \com{Zitat Frau Hegenscheid fragen}.
%%
We have to capture earlier signs of pathological change in order to derive better predictive models.
%%

@@

\subsection{Summary and Future Work}
%%
\noindent We showed, that torsion, curvature and curvature angle of the lumbar spine at the presented precision are not enough to characterize lumbar back pain in the SHIP-Data set.
%%
Our method made it possible to assess their discriminative power, which is largely limited for separating male and female subjects, nutrition variables, as well as different disease indicators.
%%
The C4.5 algorithm showed to be an effective tool for evaluating a set of derived metrics regarding their suitability to classify non-image parameters.
%%
Over-fitting to the data indicated by complex decision trees have to be taken into account into the analysis as well.
%%

In our future work, we will focus on more precise models for extracting measures described in Section~\ref{sec:ProposedFeatures}.
%%
As another focus, we want to include the method into existing visual analytics methods designed for analyzing shape information for epidemiological data \cite{Klemm2014}.
%%

Combining the power of statistical analysis, visual analytics and advanced data mining techniques is essential for analyzing increasingly complex heterogenous population data.
%%
These methods do not aim to replace the traditional epidemiological workflow, but rather intervenes at the weak points of standard statistical methods.
